{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-07 wacv_for_review.tex
Comments replied

We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target

@@

Figure \ref{fig:Filters} shows examples of three filters used in  {\it E}nKCF.

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the {\it E}nKC with hand-crafted features, dedicated to run
on low-end embedded systems, and deep features, designed to run on
the systems with GPUs. Later, we will briefly document the fundamental 
concepts of the KCF and Particle Filter, designed to smooth transitions 
between KCFs.

{\it Burak: This section does NOT connect to the previous section.}

@@

{\it Burak: I don't think that's a good way of arranging this. You
  talked about EnKCF, then KCF should come out before any variants of
  KCF w/ conventional feature and w/ deep features. Otherwise, what is
  the point of having KCF section after you explained all the usage of
  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
  deep features. Given this order, two paragraphs before and after
  this didn't connect!}

\textbf{{\it E}nKCF with Hand-Crafted Features} 
We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI.

@@

By reducing the template size of $R_{s}$,
   fluctuating run-time performances among KCFs are avoided which is desired in embedded systems.

@@

@@

>>>>

We set up {\it E}nKCF in this way because, we believe, a correlation filter for
learning a target's translation should include its background to
better discriminate the target from its surrounding, and another
correlation filter should focus on the target itself to estimate the
right scale of the target. By setting a transition filter with larger padding size, 
$R_{t}^{L}$, we can recover from potential drifts after the frames we only run the
scale filter. Additionally, we design a translation filter with smaller 
padding size, $R_{t}^{S}$, to better pinpoint target position after the 
frames we only run $R_{t}^{L}$.

@@

Since Henriques and his colleagues' presented impressive tracking
results of KCF \cite{henriques2015high} on VOT15
challenge \footnote{\url{http://www.votchallenge.net/vot2015/}}, many
variation of KCF were investigated. For example, \cite{ma2015long} and
\cite{danelljan2014accurate} used a scale filter to learn the target
area only whereas \cite{li2014scale, bibi2015multi, tang2015multi}
used a correlation filter learned on the target area and its
surrounding background in different size to learn the optimal scale of
the target. Our approach is similar to that of \cite{ma2015long} in
that more than one KCF is used to address the challenges of single
target tracking. But ours is different from their approach because we
do not use those multiple KCFs together at every frame, but
alternatively at every $k$ frame. It intuitively makes sense to
alternatively use multiple KCFs with different purposes because the
appearance of a target does not change drastically over consecutive
image frames. For most case, even it looks the appearance changes,
learning a correlation filter over consecutive frames would not be
much different from the one learned using the image few or $k$ frames
later. Figure \ref{fig:Filters_Comparison} shows examples supporting
this observation.

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

\begin{comment}
{\it Burak: This section does NOT connect to the previous section.}

@@

{\it Burak: I don't think that's a good way of arranging this. You
  talked about EnKCF, then KCF should come out before any variants of
  KCF w/ conventional feature and w/ deep features. Otherwise, what is
  the point of having KCF section after you explained all the usage of
  KCF? So, it should EnKCF, KCF, KCF w/ hand-craft features and KCF w/
  deep features. Given this order, two paragraphs before and after
  this didn't connect!}
\end{comment}

\textbf{{\it E}nKCF with Hand-Crafted Features} 
We, first, use two complimentary hand-crafted features, fHoG (shape) \cite{felzenszwalb2010object} 
and color-naming (color) \cite{li2014scale} in the {\it E}nKCF as shown in Figure \ref{fig:Filters}. 
This version of {\it E}nKCF is dedicated to perform tracking on any embedded systems at
$30$ fps, particularly on the ones without GPU units.
\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
   \\[-3ex]
\subfloat[Small Area Translation Filter]{\hspace{.30\linewidth}}\label{fig:Rt_S}
\quad\subfloat[Large Area Translation Filter]{\hspace{.37\linewidth}}\label{fig:Rt_L}
\quad\quad\subfloat[Scale Filter]{\hspace{.12\linewidth}}\label{fig:Rs}
\caption{Examples of three filters with hand-crafted features; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

The translation filter, $R_{t}^{L}$, uses both the fHoG
\cite{felzenszwalb2010object} and color-naming \cite{van2009learning}
features to learn the large background area around the target. Figure
\ref{fig:Filters}(b) shows an example of this translation filter. The
color features are also used to make the feature vector more
discriminative. In other words, for the case that the fHoG is the only
feature, the bigger the area for HoG is the more noise the resulting
fHoG feature contains. Adding color information to the feature vector
will make the feature vector more robust to the noises from the
background around the target. However, this is not the case for the
translation filter, $R_{t}^{S}$. This is because the translation filter, {\it target + small background}, 
does not contain much of the background area around the target. Figure
\ref{fig:Filters}(a) shows an example of this translation filter. 
Finally, both fHoG and color-naming features are used in the scale filter, $R_{s}$, 
The ROI considered by $R_{s}$ is resized to a smaller template resolution (64 x n) as shown in Figure~\ref{fig:Filters}(c). 
This leads to less discriminative shape features. To reduce the noise in $R_{s}$, we concatenate color features. 
The $R_{s}$ estimates the scale by correlating the filter with three candidate ROIs as detailed in
alg.~\ref{alg:MKCF}.  This increase the complexity from $\mathcal{O}(n\log n)$ to $\mathcal{O}(3(n\log n))$ for $R_{s}$. 
To reduce the number of operations, we assign a smaller template size to $R_{s}$. 
This does not degrade the tracking performance due to two reasons: (1) zero padding around the target 
and (2) integration of color features. This way, we keep the run-time complexity of
the $R_{S}$ similar to $R_{t}^{L}$ and $R_{t}^{S}$ that only run
correlation filter on a single ROI. By reducing the template size of $R_{s}$, fluctuating run-time
performances among $R_{s}$ and, $R_{t}^{L}$ and $R_{t}^{S}$, are avoided which 
is desired in embedded systems.

@@

@@

{\it YoungWoo : There are three reasons for this: (1) One is CPU and another one is GPU
implementations, I thought it would be more clear to seperate them, (2) I do not have 
results on OTB100 dataset with DeepEnKCF. (3) I believe DeepEnKCF is not the main contribution 
of this paper, showing them in the same figure with all the trackers might lead the authors to 
underestimate EnKCF.
 }

@@

{\it YoungWoo : Particle filter smoothes the translations in between the
transitions. We want to reduce drifts from scale filter by having $R_{t}^{L}$, and
we want to reduce drifts from $R_{t}^{L}$ by having $R_{t}^{S}$. The particle filter
on the other hand aims at reducing the drifts and jumps further by bringing in the 
motion information.}
